On The Impact of Atoms of Confusion in JavaScript Code

### 2021-10-16 4_Result.tex
passada inicial na secao de resultados

Finally, we also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant \emph{education} or participant \emph{experience} impact correctness. Although the results suggest that experience impacts correctness, the education level does not. As such, we replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistical difference is less significant for those developers with more than ten years of experience.

@@

\subsubsection*{The Participants' perceptions of the atom candidates}
Supporting the results of the survey, Table~\ref{tab:interview-results1}
 shows that for eight out of the
10 scenarios surveyed, the majority of the respondents prefer the version of the
code without the atom candidate.
In no case the \emph{neutral}
ratio was higher than the option for the Clean version.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Ternary Operator atom candidate the participants prefer the Confusing version, instead of the Clean one. We show the code snippets for the Ternary Operator in Figure~\ref{code:ternary}. Even for this atom candidate, some participants who preferred the left-hand side version (confusing) still believed that the right-hand side version (clean) was more readable. The following quotes were extracted from the transcripts with
% three interviewees:
two interviewees:

@@

One of the participants mentioned that the use of JavaScript's prototype-based inheritance can make it difficult to understand code, particularly when involving deep prototype chains. This is a core feature of the language, and most high-level tools and frameworks abstract it away. Although this was only mentioned by one practitioner, this is an important remark, as true understanding of JavaScript software necessarily involves understanding the concept of prototypes.

% When asked about particular JavaScript constructs or patterns that can make code difficult to understand, three participants cited the callback pattern, which can lead to several levels of nested function calls, as extremely difficult to assimilate.
When asked about particular JavaScript constructs or patterns that can make code difficult to understand, three participants cited the callback pattern---potentially leading to several levels of nested function calls---as extremely difficult to assimilate. One of the respondents stated:

@@

>>>>

{\color{blue}Finally, we also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant \emph{education} or participant \emph{experience} impact correctness. The findings suggest that \emph{developer experience} impacts on the results related to correctness (see Figure~\ref{fig:correctness-over-experience}). Even though the presence of atoms of confusion reduces the number of correct answers to all developer experience groups, this effect is not uniform. For instance, novice developers provide a higher number of wrong answers for the confusing version of the code (57.8\%), while developers with more than four years of experience provide more than 70\% of correct answers when evaluating the confusing version of the code snippets. It is also important to note that, independently of the developer experience group, developers tend to provide more than 84\% of correct answers while predicting the outputs for the clean versions of the code.} {\color{red}We replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistical difference is less significant for those developers with more than ten years of experience.} Differently from developer experience, the factor \emph{education level} does not change substantially the correctness of the answers.

\begin{figure}
  \includegraphics[scale=0.35]{images/correctness-by-experience}
  \caption{Impact of atoms of confusion on the correctness (over the developer experience groups)}
  \label{fig:correctness-over-experience}
\end{figure}

@@

\subsubsection*{The Participants' perceptions of the atom candidates}
Supporting the results of the survey, Table~\ref{tab:interview-results1}
 shows that for eight out of the
10 scenarios surveyed, the majority of the respondents prefer the version of the
code without the atom candidate.
In no case the \emph{neutral}
ratio was higher than the option for the clean version.
%% An example entry is contained in Appendix~\ref{}. 
%% For a full listing of the code snippets, visit the paper repository. 
Only for the Ternary Operator atom candidate the participants prefer the Confusing version, instead of the clean one. We show the code snippets for the Ternary Operator in Figure~\ref{code:ternary}. Even for this atom candidate, some participants who preferred the left-hand side version (confusing) still believed that the right-hand side version (clean) was more readable. The following quotes were extracted from the transcripts with
% three interviewees:
two interviewees:

@@

One of the participants mentioned that the use of JavaScript's prototype-based inheritance can make it difficult to understand code, particularly when involving deep prototype chains. This is a core feature of the language, and most high-level tools and frameworks abstract it away.
%Although this was only mentioned by one practitioner, this is an important remark, as true understanding of JavaScript software necessarily involves understanding the concept of prototypes.
% When asked about particular JavaScript constructs or patterns that can make code difficult to understand, three participants cited the callback pattern, which can lead to several levels of nested function calls, as extremely difficult to assimilate.
When asked about particular JavaScript constructs or patterns that can make code difficult to understand, three participants cited the callback pattern---potentially leading to several levels of nested function calls---as extremely difficult to assimilate. One of the respondents stated:

@@

\todo[inline]{Seria legal contrastar esses achados com o que foi reportado anteriormente}
